An Improved ANS Transaction Template

### 2018-01-26 paper.tex

\subsection{Relevant Cases}
\subsubsection{Reference Case}
The reference case corresponds to the most ideal cascade design--utilizing all of the 5060
centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assays are respectively
0.0071/0.903/0.0028.
%maybe include some cascade shape figures?

@@

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}
Despite the reconfiguration of each level occurring in the second case, the case
1 is notably more effective in producing HEU than case 1. Indeed, as observed in Figure
\ref{fig:assay_c1_nc} and \ref{fig:assay_c2_nc}, the first case is able to
produce an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$ with the same number of levels.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 without recycling.}\label{fig:assay_c1_nc}
\end{figure}
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 without recycling.}\label{fig:assay_c2_nc}
\end{figure}

@@

\bottomrule \end{tabular} \caption{Cascade effective $\theta$ as a function of
the cascade level and the case considered.} \label{tab:cascade_theta}
\end{table} As illustrated in Table \ref{tab:cascade_theta}, the effective cut
of each level increases up to $0.54$ for the fifth stage for case 2. The high
effective cut value increase the product production rate but decrease the
enrichment ratio.

\subsubsection{tails recycling}

\subsubsection{Case 1}
As shows on Figure \ref{ }, without tails recycling, the number of cascade levels
required to enrich uranium up to $90\%$ is 5 for the
first case considered. Recycling the tails allows for a reduction in the number of
enrichment levels down to only 3.

This bump in enrichment can easily be explained, as the cascade does not have
the same number of stages, less work is spent on stripping as opposed to
enriching. Even compared to an ideal case, where the stripping
work of a stage is the exact inverse of the enriching work, a cascade with
less stripping stages will produce tails with a higher
enrichment than the feed of the previous level of

%Did you commit in the middle of a sentence or did you forget to finish?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Analysis}

>>>>

\subsection{Explored Cases}
\subsubsection{Reference Case}
The reference case corresponds to the most ideal cascade design--utilizing all of the 5060
centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assays are respectively
0.0071/0.903/0.0028.
%maybe include some cascade shape figures?

@@

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}
Despite the reconfiguration of each level occurring in the second case, the case
1 is notably more effective in producing HEU than case 1. Indeed, as observed in Figure
\ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able to
produce an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$ with the same number of levels.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 without recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c1_nr}
\end{figure}
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 without recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c2_nr}
\end{figure}

@@

\bottomrule
\end{tabular}
  \caption{Cascade effective $\theta$ by the level and case.}
  \label{tab:cascade_theta}
\end{table}
\end{table} 
As illustrated in Table \ref{tab:cascade_theta}, the effective cut
of each level increases up to $0.54$ for the fifth stage for case 2. The high
effective cut value increase the product production rate but decrease the
enrichment ratio.

\subsubsection{tails recycling}
When recycling the tails from the different cascade levels, both cases behave
the same way. As the tails have an higher enrichment than the product then are
blended to, recycling the tail has the effect to bump up the enrichment of the
product at each level (see Figure \ref{fig:assay_c1_r} and \ref{fig:assay_c2_r}).

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 with recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c1_r}
\end{figure}

Note that for the case 2, where the fourth stage could appear as useless only the
blending of its tail allows the product of the third one to pass the $90\%$ threshold.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 with recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c2_r}
\end{figure}

\subsection{HEU flow rate}
